\huge Tor's Usability for Censorship Circumvention

### 2016-05-07 pets2017-paper/pets2017-paper.tex
Dump time_to_success_active_clamped into the paper.
comment out error discussion from success rate

\begin{figure}[t]
\centering
\includegraphics[width=.5\textwidth]{warning.png}
\caption{
A screenshot of the interface with the ``Copy Tor Log to Clipboard'' button, 
which appears silently and does not interrupt the progress bar. 
This warning was generated by entering in syntactically correct but invalid proxy settings,
a mistake that prevents users from ever connecting to the Tor network. 
Users are never directly notified of this error through an error message or a timeout message.
Our participants made this error during our experiments, along with others that they were not notified about. 
}
\label{fig:warning}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=.5\textwidth]{log-messages.png}
\caption{
The last 24 of 45 log lines that users receive after clicking clicking the ``Copy Tor Log to Clipboard'' button. 
These log lines were the result of entering in syntactically correct but invalid proxy settings,
a mistake that prevents users from ever connecting to the Tor network. Understanding the Tor logs require
technical expertise from the user to understand the logs, diagnose the problem, and formulate next steps.
}
\label{fig:warning_log}
\end{figure}

We believe that the added advice on what to try next on error messages would have improved the rate of success. However, only 1 of 116 participants saw an error during the experiment. The old interface warned users on some mistakes (i.e. entering in a syntactically correct but invalid proxy settings) rather than displaying an error message. When a user receives a warning, a button that says ``Copy Tor Log to Clipboard'' silently appears at the bottom of the interface (Figure~\ref{fig:warning}). To see the log messages, users must click on the button, open up a text editor, and paste the log messages. The log messages require the user to understand the log, diagnose the problem, and formulate next steps (Figure~\ref{fig:warning_log}).

That participant was using the new interface and was told that the bridge configuration was the source of the error. The participant heeded the interface's advice to reconfigure the bridge options. But since most participants did not see any error messages, any effects they may have had on success rates are not reflected in our results. The addition of a summary screen did cause behavioral changes (13\% of participants saw their current settings, then went back and adjusted them), but this behavioral change did not have a statistically significant impact on success rates.

>>>>

%\begin{figure}[t]
%\centering
%\includegraphics[width=.5\textwidth]{warning.png}
%\caption{
%A screenshot of the interface with the ``Copy Tor Log to Clipboard'' button, 
%which appears silently and does not interrupt the progress bar. 
%This warning was generated by entering in syntactically correct but invalid proxy settings,
%a mistake that prevents users from ever connecting to the Tor network. 
%Users are never directly notified of this error through an error message or a timeout message.
%Our participants made this error during our experiments, along with others that they were not notified about. 
%}
%\label{fig:warning}
%\end{figure}

%\begin{figure}[t]
%\centering
%\includegraphics[width=.5\textwidth]{log-messages.png}
%\caption{
%The last 24 of 45 log lines that users receive after clicking clicking the ``Copy Tor Log to Clipboard'' button. 
%These log lines were the result of entering in syntactically correct but invalid proxy settings,
%a mistake that prevents users from ever connecting to the Tor network. Understanding the Tor logs require
%technical expertise from the user to understand the logs, diagnose the problem, and formulate next steps.
%}
%\label{fig:warning_log}
%\end{figure}
%
%We believe that the added advice on what to try next on error messages would have improved the rate of success. However, only 1 of 116 participants saw an error during the experiment. The old interface warned users on some mistakes (i.e. entering in a syntactically correct but invalid proxy settings) rather than displaying an error message. When a user receives a warning, a button that says ``Copy Tor Log to Clipboard'' silently appears at the bottom of the interface (Figure~\ref{fig:warning}). To see the log messages, users must click on the button, open up a text editor, and paste the log messages. The log messages require the user to understand the log, diagnose the problem, and formulate next steps (Figure~\ref{fig:warning_log}).
%
%That participant was using the new interface and was told that the bridge configuration was the source of the error. The participant heeded the interface's advice to reconfigure the bridge options. But since most participants did not see any error messages, any effects they may have had on success rates are not reflected in our results. The addition of a summary screen did cause behavioral changes (13\% of participants saw their current settings, then went back and adjusted them), but this behavioral change did not have a statistically significant impact on success rates.
